### 2019-01-25 journal/experiments.tex
ok

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.

>>>>

A deterministic alternative to random sampling, long used in the mutation testing community, is operator-based selection, where only some mutation operators are applied \cite{wong1995reducing,untch2009onreduced}.  Using \emph{only statement deletion and condition negation mutants}, as in our toy example, on the grounds that we expect most compiler ``repairs'' to simply avoid an optimization, not actually fix a simple defect such as an off-by-one error in a loop, is an intuitively appealing and trivial to implement approach.  The idea is clearly related to the object-level branch-mutation proposed above, conceptually, but operating at the (more understandable to humans, and thus useful in localization) source level.  The resulting cost reduction is significant:  67.8\% of mutants can be ignored for SpiderMonkey, and 73\% for GCC.  More importantly, the APFD actually \emph{improves} with this change.  For SpiderMonkey, the APFD improves by almost 3\%, and for GCC, it improves by 0.86\%.  For SpiderMonkey, the early curve (first ten items) is improved, and for GCC it is very slightly worse.  Most importantly, in both cases, two additional faults are revealed in the first 50 examined tests.  Operator selection can make a difference for fault localization, but with hot mutants, it is easy, if localization using only negations and deletions is not helpful, run all mutants on the test to be localized, then run only the small set of repairing mutants on other tests to compute the same localization as with the full set of operators, since most tests are repaired by only a few mutants.
